### 2022-07-11 sections/awards.tex
Update awards.tex

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowance for participation in conferences and purchase of books, {\pounds} 2,225} 
{Oxford, UK}
{2022}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2,255} 
{Oxford, UK}
{2022}
\end{cvhonors}
